---
title: "Homework 1"
author: "mehmet özden 19080409!"
---

```{r global_options, include=FALSE}
# Do not delete or modify this chunk.
# We will cover chunk options later.
# This is required for Question 7
library(knitr)
opts_chunk$set(fig.align="center", fig.height=4, fig.width=5.5)
```

**Question 1** With Markdown write a sentence that has one word in bold.


I  write  my **sentences** here !


**Question 2** With Markdown write a sentence that has one word in italic.

I  write  my _sentences_ here!

**Question 3** With Markdown write a sentence that has one word in italic bold.

I  write  my  **_sentences_** here!

**Question 4** With Markdown write an unordered list with three items.

* Item 1
* Item 2
* Item 3


**Question 5** With Markdown write an ordered list with three items.

Here's an example of an ordered list in Markdown:

1. Item 1
2. Item 2
3. Item 3




**Question 6** With Markdown give a link to your favorite webpage.

[youtube](http://youtube.com)!

**Question 7** With Markdown add a cat picture.

[cat](http://en.wikipedia.org/wiki/Cat)!

**Question 8** With Rmarkdown insert a code chunk and give an example of a simple mathematical calculation in it.

```{r}
# Calculation
3 + 5 * 2
```


**Question 9** With $LaTeX$ write your favorite equation in block form.

library(knitr)
opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE)
$$
A = \pi r^2
$$
!

**Question 10** In a code chunk calculate 3 + 4.
```{r}
# Calculation
3 + 4
```
